\documentclass[12pt, letterpaper]{article}
\usepackage{geometry}
\usepackage{mathptmx}
\geometry{letterpaper, margin=.5in, nohead, nofoot}
\newcommand\mybar{\kern1pt\rule[-\dp\strutbox]{.8pt}{\baselineskip}\kern1pt}

\begin{document}
	\begin{flushleft}
		\textbf{\large Xeryus Matthew Velasco}\\
		Stanton, CA 90680\\
		(909) 518-7464 $\vert$ xeryusvelasco@gmail.com\\
		github.com/xeryus-velasco $\vert$ linkedin.com/in/xeryus-velasco\vspace{5mm}
		
\textbf{\large Summary}\\
Highly motivated software engineering student pursuing a bachelors degree in computer science with a minor in mathematics. Focused and dedicated with a desire to gain a strong technical foundation. Seeking an entry-level role within a software firm where success is paramount and learning is encouraged.\vspace{5mm}

\textbf{\large Education}\\
California State Polytechnic University, Pomona\hfill Expected Graduation: June 2021\\
Bachelor of Science in Computer Science\hfill Current GPA: 3.29\\
Minoring in Mathematics\vspace{5mm}

\textbf{\large Personal Projects}\\
\begin{itemize}
	\item Spoofing and sniffing packets through \textit{pcap} C library, \textit{scapy} Python library, and Wireshark.
	\item SYN Flooding attack, TCP Reset Attack, and TCP session Hijacking 
	\item Cross Site Scripting Attacks and methods to clean code from users properly 
	\item SQL Injection Attacks and how to prevent them efficiently
\end{itemize}
All of these \textit{hacks} were done through virtual machines on a VM network with caution in mind.\vspace{5mm} 

\textbf{\large Employment History}\\
Autologue Computer Systems\hfill Buena Park, CA\\
\textit{Junior Software Engineer}\hfill June 2018 - Current
\begin{itemize}
  \item Produced clean and cohesive code for tasks with proper documentation and comments.
  \item Wrote unit tests with NUnit and Selenium through Visual Studio.
  \item Light front-end web development with Bootstrap 4.
\end{itemize}

\textbf{\large Skills}
\begin{itemize}
	\item Intermediate comprehension of
	\begin{itemize}
		\item C\#
		\item C++
		\item Python
		\item Java
	\end{itemize}
	\item Experience in both Windows and Linux development environment.
	\item Moderate understanding of bash.
	\item Git / SVC
\end{itemize}

\end{flushleft}
	
\end{document}
